---
title: "Buoy"
author: "Simu Huang"
date: "2020/9/25"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Import data
 
  The first step is to download the data from 2000 to 2019 on the NDBC. in these data, the variable types are not exactly the same from year to year, we need to delete some columns, such as the variable tide and the duplicate variable mm. Then, we connect the year's data together to get a data frame that contains all the data.

```{r cars}
library(data.table)
library(tidyverse)
library(lubridate)
library(citation)
setwd("D:\\Documents\\R Project\\615\\buoy project\\data")

#2000
Buoy2000<-read.csv("buoy2000.txt",sep="",header = T)
Buoy2000$TIDE<-0
Buoy2000$mm<-0
colnames(Buoy2000)[1]<-"X.YY"
colnames(Buoy2000)[5]<-"WDIR"
colnames(Buoy2000)[12]<-"PRES"

#2001
Buoy2001<-read.csv("buoy2001.txt",sep="",header = T)
Buoy2001$mm<-0
colnames(Buoy2001)[1]<-"X.YY"
colnames(Buoy2001)[5]<-"WDIR"
colnames(Buoy2001)[12]<-"PRES"


#2002
Buoy2002<-read.csv("buoy2002.txt",sep="",header = T)
Buoy2002$mm<-0
colnames(Buoy2002)[1]<-"X.YY"
colnames(Buoy2002)[5]<-"WDIR"
colnames(Buoy2002)[12]<-"PRES"

#2003
Buoy2003<-read.csv("buoy2003.txt",sep="",header = T)
Buoy2003$mm<-0
colnames(Buoy2003)[1]<-"X.YY"
colnames(Buoy2003)[5]<-"WDIR"
colnames(Buoy2003)[12]<-"PRES"

#2004
Buoy2004<-read.csv("buoy2004.txt",sep="",header = T)
Buoy2004$mm<-0
colnames(Buoy2004)[1]<-"X.YY"
colnames(Buoy2004)[5]<-"WDIR"
colnames(Buoy2004)[12]<-"PRES"

#2005
Buoy2005<-read.csv("buoy2005.txt",sep="",header = T)
mm2005<-Buoy2005$mm
Buoy2005$mm<-NULL
Buoy2005$mm<-mm2005
colnames(Buoy2005)[1]<-"X.YY"
colnames(Buoy2005)[5]<-"WDIR"
colnames(Buoy2005)[12]<-"PRES"

#2006
Buoy2006<-read.csv("buoy2006.txt",sep="",header = T)
mm2006<-Buoy2006$mm
Buoy2006$mm<-NULL
Buoy2006$mm<-mm2006
colnames(Buoy2006)[1]<-"X.YY"
colnames(Buoy2006)[5]<-"WDIR"
colnames(Buoy2006)[12]<-"PRES"

#2007
Buoy2007<-read.csv("buoy2007.txt",sep="",header = T)
mm2007<-Buoy2007$mm
Buoy2007$mm<-NULL
Buoy2007$mm<-mm2007
Buoy2007 = Buoy2007[-c(1),]

#2008
Buoy2008<-read.csv("buoy2008.txt",sep="",header = T)
mm2008<-Buoy2008$mm
Buoy2008$mm<-NULL
Buoy2008$mm<-mm2008
Buoy2008 = Buoy2008[-c(1),]


#2009
Buoy2009<-read.csv("buoy2009.txt",sep="",header = T)
mm2009<-Buoy2009$mm
Buoy2009$mm<-NULL
Buoy2009$mm<-mm2009
Buoy2009 = Buoy2009[-c(1),]

#2010
Buoy2010<-read.csv("buoy2010.txt",sep="",header = T)
mm2010<-Buoy2010$mm
Buoy2010$mm<-NULL
Buoy2010$mm<-mm2010
Buoy2010 = Buoy2010[-c(1),]

#2011
Buoy2011<-read.csv("buoy2011.txt",sep="",header = T)
mm2011<-Buoy2011$mm
Buoy2011$mm<-NULL
Buoy2011$mm<-mm2011
Buoy2011 = Buoy2011[-c(1),]

#2012
Buoy2012<-read.csv("buoy2012.txt",sep="",header = T)
mm2012<-Buoy2012$mm
Buoy2012$mm<-NULL
Buoy2012$mm<-mm2012
Buoy2012 = Buoy2012[-c(1),]

#2013
Buoy2013<-read.csv("buoy2013.txt",sep="",header = T)
mm2013<-Buoy2013$mm
Buoy2013$mm<-NULL
Buoy2013$mm<-mm2013
Buoy2013 = Buoy2013[-c(1),]

#2014
Buoy2014<-read.csv("buoy2014.txt",sep="",header = T)
mm2014<-Buoy2014$mm
Buoy2014$mm<-NULL
Buoy2014$mm<-mm2014
Buoy2014 = Buoy2014[-c(1),]

#2015
Buoy2015<-read.csv("buoy2015.txt",sep="",header = T)
mm2015<-Buoy2015$mm
Buoy2015$mm<-NULL
Buoy2015$mm<-mm2015
Buoy2015 = Buoy2015[-c(1),]

#2016
Buoy2016<-read.csv("buoy2016.txt",sep="",header = T)
mm2016<-Buoy2016$mm
Buoy2016$mm<-NULL
Buoy2016$mm<-mm2016
Buoy2016 = Buoy2016[-c(1),]

#2017
Buoy2017<-read.csv("buoy2017.txt",sep="",header = T)
mm2017<-Buoy2017$mm
Buoy2017$mm<-NULL
Buoy2017$mm<-mm2017
Buoy2017 = Buoy2017[-c(1),]

#2018
Buoy2018<-read.csv("buoy2018.txt",sep="",header = T)
mm2018<-Buoy2018$mm
Buoy2018$mm<-NULL
Buoy2018$mm<-mm2018
Buoy2018 = Buoy2018[-c(1),]

#2019
Buoy2019<-read.csv("buoy2019.txt",sep="",header = T)
mm2019<-Buoy2019$mm
Buoy2019$mm<-NULL
Buoy2019$mm<-mm2019
Buoy2019 = Buoy2019[-c(1),]

#Combine

Buoy<-rbind(Buoy2000,Buoy2001,Buoy2002,Buoy2003,Buoy2004,Buoy2005,Buoy2006,Buoy2007,Buoy2008,Buoy2009,Buoy2010,Buoy2011,Buoy2012,Buoy2013,Buoy2014,Buoy2015,Buoy2016,Buoy2017,Buoy2018,Buoy2019)

```

## 
There are some outliers, like temperatures above 50 degrees and some observations of 999. These are obviously not practical. Therefore, we only choose the observations meeting our requirements to create a new date set. 


```{r}

Buoy[Buoy==99|Buoy==999|Buoy==9999]<-0

Buoy <- Buoy [, -11]
Buoy <- Buoy [, -15:-17]

#remove outliers
a <- Buoy %>% select(X.YY, MM, DD, hh)

a2 <- as.data.frame(lapply(a,as.numeric))
D_date<- make_datetime(year=a2$X.YY, month=a2$MM, day=a2$DD, hour=a2$hh)
Buoy$D_date <- D_date
cols <- colnames(Buoy)
new_cols <- c(cols[1], cols[length(cols)], cols[2:(length(cols) - 1)])
Buoy <- Buoy[, new_cols]
Buoy <- Buoy[,c(-1,-3:-5)]
Buoy <- filter(Buoy, DEWP < 999 & ATMP < 50 & WTMP < 50)
Buoy$D_date <- as.POSIXct(Buoy$D_date)
Buoy[,2:11]<-lapply(Buoy[,2:11],as.numeric)

save(Buoy, file = "Buoy.Rdata")
```


##
We think it is possible to compare the change in temperature according to the average monthly and yearly temperature. In this step, we reorder the data by date, month and year and calculate the mean value of these data, because in this way, We can use the average daily temperature to conclude the temperature trend, and the average monthly temperature and the average annual temperature can eliminate the influence of seasons and extreme weather on the results.


```{r}
Buoy <- filter(Buoy, DEWP < 999 & ATMP < 50 & WTMP < 50)
Buoy$D_date <- as.POSIXct(Buoy$D_date)
Buoy[,2:11]<-lapply(Buoy[,2:11],as.numeric)

Buoy2 <- Buoy %>% group_by(date(D_date)) %>% summarize(mean(WDIR),mean(WSPD),mean(GST),mean(WVHT),mean(DPD),mean(APD),mean(PRES),mean(ATMP),mean(WTMP),mean(DEWP))

Buoy3 <- Buoy %>% group_by(year(D_date),month(D_date)) %>% summarize(mean(WDIR),mean(WSPD),mean(GST),mean(WVHT),mean(DPD),mean(APD),mean(PRES),mean(ATMP),mean(WTMP),mean(DEWP))

Buoy4 <- Buoy %>% group_by(year(D_date)) %>% summarize(mean(WDIR),mean(WSPD),mean(GST),mean(WVHT),mean(DPD),mean(APD),mean(PRES),mean(ATMP),mean(WTMP),mean(DEWP))

b <- Buoy3 %>% select(`year(D_date)`,`month(D_date)`)
b2 <- as.data.frame(lapply(b,as.numeric))
year_month <- make_date(year = b$`year(D_date)`,month = b$`month(D_date)`)
Buoy3$year_month<-year_month

```


##
#ATMP
As the simple regression model, we can find that for each year of time increase, the predicted annual increase in air temperature is 0.099, which means that the global warming is indeed happening. And we find that the relationship between averaged wind speed over the an eight-minute period and the dominant wave period is not obvious so we delete these two variable. The two factors that best reflect change are the gust speed(GST) and the wind speed (WSPD).

#WTMP
In this model, we can find that for each year of time increase, the predicted annual increase in sea surface temperature is 0.1155, which also indicates that the global warming is indeed happening. And we find that the relationship between averaged wind speed over the an eight minute period, wind direction, and the dominant wave period is not obvious so we delete these three variable. The two factors that best reflect change is the wind speed (WSPD).


```{r}


#ATMP
fit_in <- lm (Buoy4$`mean(ATMP)` ~ Buoy4$`year(D_date)`)
fit_year <- lm ( Buoy4$`mean(ATMP)` ~ Buoy4$`mean(WDIR)`+ Buoy4$`mean(WSPD)`+Buoy4$`mean(GST)`+ Buoy4$`mean(WVHT)`+ Buoy4$`mean(APD)` , data = Buoy4 )
fit_month <- lm ( Buoy3$`mean(ATMP)` ~ Buoy3$`mean(WDIR)`+ Buoy3$`mean(WSPD)`+Buoy3$`mean(GST)`+ Buoy3$`mean(WVHT)`+ Buoy3$`mean(APD)` , data = Buoy3 )
fit_day <- lm ( Buoy2$`mean(ATMP)` ~ Buoy2$`mean(WDIR)`+ Buoy2$`mean(WSPD)`+Buoy2$`mean(GST)`+ Buoy2$`mean(WVHT)`+ Buoy2$`mean(APD)` , data = Buoy2 )

print(fit_in)
print(fit_year)
print(fit_month)
print(fit_day)
plot(fit_in)
plot(fit_year)
plot(fit_month)
plot(fit_day)
summary(fit_in)
summary(fit_year)
summary(fit_month)
summary(fit_day)


ggplot(mapping = aes(x= `year(D_date)`, y= `mean(ATMP)`),data = Buoy4)+ geom_point() + geom_smooth(method = "lm", color="black", formula = y ~ x)

ggplot(mapping = aes(x= year_month, y= `mean(ATMP)`),data = Buoy3)+ geom_point() + geom_smooth(method = "lm", color="black", formula = y ~ x)

ggplot(mapping = aes(x= `date(D_date)`, y= `mean(ATMP)`),data = Buoy2)+ geom_point() + geom_smooth(method = "lm", color="black", formula = y ~ x)


#WTMP
fit_in_1 <- lm (Buoy4$`mean(WTMP)` ~ Buoy4$`year(D_date)`)
fit_year_1 <- lm ( Buoy4$`mean(WTMP)` ~  Buoy4$`mean(WSPD)`+Buoy4$`mean(GST)`+ Buoy4$`mean(WVHT)`+ Buoy4$`mean(APD)` , data = Buoy4 )
fit_month_1 <- lm ( Buoy3$`mean(WTMP)` ~  Buoy3$`mean(WSPD)`+Buoy3$`mean(GST)`+ Buoy3$`mean(WVHT)`+ Buoy3$`mean(APD)` , data = Buoy3 )
fit_day_1 <- lm ( Buoy2$`mean(WTMP)` ~  Buoy2$`mean(WSPD)`+Buoy2$`mean(GST)`+ Buoy2$`mean(WVHT)`+ Buoy2$`mean(APD)` , data = Buoy2 )

print(fit_in_1)
print(fit_year_1)
print(fit_month_1)
print(fit_day_1)
plot(fit_year_1)
plot(fit_month_1)
plot(fit_day_1)
summary(fit_in_1)
summary(fit_year_1)
summary(fit_month_1)
summary(fit_day_1)


ggplot(mapping = aes(x= `year(D_date)`, y= `mean(WTMP)`),data = Buoy4)+ geom_point() + geom_smooth(method = "lm", color="blue", formula = y ~ x)

ggplot(mapping = aes(x= year_month, y= `mean(WTMP)`),data = Buoy3)+ geom_point() + geom_smooth(method = "lm", color="blue", formula = y ~ x)

ggplot(mapping = aes(x= `date(D_date)`, y= `mean(WTMP)`),data = Buoy2)+ geom_point() + geom_smooth(method = "lm", color="blue", formula = y ~ x)

package2zenodo("citation")
```


